### 2021-07-21 doc/thesis/chapters/hls.tex
workflow done

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Workflow}

@@

  \item \textbf{Co-Simulation}\\
      Co-Simulation serves the purpose verify the correct functionality of the generated RTL code.
      However, the main goal is not to verify the algorithm here.
      This is already done by above described C simulation.

  \item \textbf{integrate the generated RTL to a larger FPGA design}\\
  \item \textbf{synthesize FPGA bitstream}\\
  \item \textbf{use on FPGA}\\
\end{itemize}

@@

An HLS testbench can be executed in different levels of abstraction, which is a major difference between a VHDL testbench and an HLS testbench.
The most important impact thereof is the execution speed - the time it takes to simulate a number of test cases on the DUT.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Workflow}
\label{sec:hls:workflow}

@@

  \item \textbf{Co-Simulation}\\
      Co-Simulation serves the purpose to verify the correct functionality of the generated RTL code.
      It is not the goal to verify the algorithm, though.
      This is already done in the previous C simulation step.
      However, the issue is that the C simulation is executed like a regular program, which means it is executed sequentially, instruction by instruction and thus parallelism cannot be represented.\\

      This is where the Co-Simulation becomes neccessary.
      The RTL code is simulated with an HDL simulator software, which can actually simulate the parallelism as it exists in the FPGA hardware.
      In that way it can be ensured, that the user did not break the functional correctness of the algorithm, by giving wrong parallelization guidance to the HLS tool.\\

      The external simulator software has to run the complex HDL simulation and return data results, which is a time consuming task.
      Therefore, the execution time of this simulation type is expected to be approximately 10.000 times slower, compared to the C simulation.\\

  \item \textbf{Integration of the generated IP}\\
      At this point, the developed HLS code is fully verified and can successfully be transformed into working RTL code.
      Xilinx HLS exports the generated RTL code in an IP structure that is supported by its IP integrator tool, that is used in Vivado or Vitis.
      Therefore, the developed IP core can be imported to the block design as another processing block, get connected with other IPs, and in that way get integrated into a larger design.\\

  \item \textbf{Synthesize FPGA bitstream}\\
      Like in any other FPGA development cycle, the created block design can now be synthesized.
      This generates a bitstream file, which can be programmed into an actual FPGA hardware.
      Depending on the architecture of the system, the developed IP may now interface with the on-chip CPU, in the example of a System-On-Chip.\\
\end{itemize}

These steps represent the standard workflow for the development of an integrated HLS IP.
A successful deployment on hardware can be achieved if they are completed accurately.
There may be more and deeper knowledge necessary, in order to use this design approach.
This thesis however focuses on system design, not on HLS specifically, and thus a comprehensive study of the referenced literature is recommended.

@@

An HLS testbench can be executed in different levels of abstraction, which is a major difference between a VHDL testbench and an HLS testbench.
The most important impact thereof is the execution speed - the time it takes to simulate a number of test cases on the DUT.\\

Section \ref{sec:hls:workflow} above already mentioned the topic of testbenches.
The following descriptions are a comprehensive extension around this topic and the simulation types.
